Cryptographic assurance of secrecy and fairness in voting

### 2012-12-07 paper/paper.tex
line breaks
Finished the section on secrecy

% setup
\documentclass[10pt,twocolumn]{article}
\usepackage{abstract}
\usepackage[hypcap]{caption}
\usepackage{color}
\usepackage{enumerate}
\usepackage{fullpage}
\usepackage{graphicx}
\usepackage{hyperref}
\usepackage{microtype}
\nonstopmode

@@

% custom commands
\newcommand{\todo}[1]{\textcolor{red}{\textbf{TODO:} \emph{#1}}}
\newcommand{\term}[1]{\textit{#1}}
\newcommand{\bterm}[1]{\textbf{\textit{#1}}}
\newcommand{\code}[1]{\texttt{#1}}
\newcommand{\super}[1]{\textsuperscript{#1}}
\newcommand{\sub}[1]{\textsubscript{#1}}
\newcommand{\preta}{Pr\^{e}t \`{a}}
\newcommand{\pv}{\preta{} Voter}

@@

\cite{delaune} enumerates a hierarchy of ballot secrecy definitions.
In order of increasing strength, they are
\term{privacy}, \term{receipt-freeness}, and \term{coercion resistance}.

@@

\cite{kremer} gives an \term{observational equivalence} definition of privacy:
An election system is private if an attacker, having access to the public
information published by the polling authority, ``cannot distinguish
the actual situation from one in which two voters have swapped their votes.''

% For all pairs of voters $v_1$, $v_2$ ...

@@

@@

\subsection{Stuff that will be moved into one of the previous sections}

Countries such as the United States hold as a fundamental right that voting can be performed
in secret to reduce the possibility of voter coercion from any private entities.
In some developing states where corruption is prevalent, it may be desirable keep an
individual's vote hidden even from the election authority, again for the reason of
limiting coercibility. The latter goal is significantly more restrictive.

Ballot secrecy, often referred to as \term{receipt-freeness}, is perhaps the most complicated
security goal to address in a verifiable voting system.
Secrecy and verifiability are naturally at odds, and only through cryptography can we
reconcile these two requirements.

Amidst these other goals, it becomes difficult to prevent \term{coercion}: the ability of some party
to coerce a voter to vote for a particular candidate.

With conventional in-person voting, coercion is thwarted to some extent by the physical security
imposed at polling locations: a party cannot \emph{watch} a voter cast a ballot and so cannot rest
assured that the voter did as told.

Though ballot secrecy prevents such a party from determining that a voter has done as asked, it is a
different problem to ensure that even the voter herself cannot prove that her ballot was
cast a certain way. We show, in describing these systems, that the cryptographic techniques
used to provide ballot secrecy also ensure -- in the case of in-person elections -- that a voter
cannot prove her ballot was cast a certain way even with the data necessarily exposed to provide
verifiability.

>>>>

% setup
\documentclass[10pt,twocolumn]{article}
\usepackage{abstract}
\usepackage[hypcap]{caption}
\usepackage{color}
\usepackage{enumerate}
\usepackage{fullpage}
\usepackage{graphicx}
\usepackage{hyperref}
\usepackage{microtype}
\usepackage{amsmath}
\nonstopmode

@@

% custom commands
\newcommand{\todo}[1]{\textcolor{red}{\textbf{TODO:} \emph{#1}}}
\newcommand{\term}[1]{\textit{#1}}
\newcommand{\bterm}[1]{\textbf{\textit{#1}}}
\newcommand{\code}[1]{\texttt{#1}}
\newcommand{\super}[1]{\textsuperscript{#1}}
\newcommand{\sub}[1]{\textsubscript{#1}}
\newcommand{\preta}{Pr\^{e}t \`{a}}
\newcommand{\pv}{\preta{} Voter}
\newcommand{\abs}[1]{\ensuremath{\left\vert#1\right\vert}}

@@

\cite{delaune} enumerates a hierarchy of ballot secrecy definitions.
In order of increasing strength, they are
\term{privacy}, \term{receipt-freeness}, and \term{coercion resistance}.
Countries such as the United States hold voting privacy as a fundamental right,
and under traditional voting systems, privacy implies coercion resistance.
For more complicated systems, however, we will need to explicitly discuss
stronger formalizations of coercibility.

@@

A tempting notion of privacy would be to suggestion that it ought to be impossible
to determine any fact about a voter's vote. As \cite{preta} notes, however,
this is impossible to achieve, as demonstrated by the case of a unanimous election,
in which case every vote is trivially known.
\cite{kremer} gives an \term{observational equivalence} definition of privacy:
An election system is private if an attacker, having access to the public
information published by the polling authority, ``cannot distinguish
the actual situation from one in which two voters have swapped their votes.''
This notion is formalized using a process calculus such as the pi calculus.

Another intuition which we will find useful in discussion of the Scantegrity II system is:
Assume a list of votes $a_1, a_1, \ldots, a_n$ is public, and the mapping between
voters and votes is described by a secret permutation $\pi_k$ such that the vote
belonging to voter $v_i$ is $a_{\pi_k(i)}$.
As long as an attacker cannot gain information about $\pi_k$,
the system reveals no more information than is implies by an anonymized list of votes.

Note that privacy does not necessarily imply that votes are hidden from the election
authority. In some developing states where corruption is prevalent, this may be desirable,
again for the purpose of limiting coercibility.
This requirement is significantly more restrictive, however, and is not addressed by
any systems under our discussion.

@@

With conventional in-person voting, privacy provided by physical security imposed
at polling locations is sufficient to ensure secrecy.
A party who cannot \emph{watch} a voter cast a ballot and cannot know what vote
was cast, because traditional systems have no need to retain any information
beyond the vote itself.
Receipt-freeness, however, is a complication added by verifiable voting system.
Secrecy and verifiability are naturally at odds, and only through cryptography can we
reconcile these two requirements.

Receipt-freeness implies that even if a voter wants to tell a coercer that
she has cast a particular vote, she is necessarily unable to prove it.

@@

Coercion resistance means that secrecy is maintained even if interaction
with the coercer is allowed throughout the voting process.
The distinction between receipt-freeness and coercion resistance is subtle,
and is commonly often lost in ambiguity due to a lack of formal definitions. \cite{delaune}
In some verifiable voting systems, receipt-freeness directly implies coercion resistance,
but this is not necessarily the case.

Even in a receipt-free system,
if the voting process involves a multi-step iteraction involving the coercer,
it may be possible for the voter to prove to the coercer that she is following
some protocol. \cite{delaune}
A simple example that is common to many proposed voting systems is
the \term{Italian attack}. \cite{preta}
This problem arises when the ballot contains a large number of voting options,
such as a ranked election in which the number of possibilities grows as the
factorial of the number of candidates.
If the voter and coercer have one interaction prior to voting,
they can follow this protocol:
\begin{enumerate}
\item A coercer who favors candidate $c_1$ randomly permutes $[2, n]$ and
communicates the resulting permutation $\pi$ to the voter.
\item The voter casts a ballot ranking candidates in the order
$c_1, c_{\pi(2)}, c_{\pi(3)}, \ldots$.
\item The coercer, seeing the resulting ballot in the published list of votes,
is assured that it was cast by the voter with probability
$\ge 1 - \frac{1}{(n-1)!}$.
\end{enumerate}
